---
title: "DV_RProject3"
author: "Probe, Yudkin, Honganen"
date: "Wednesday, March 4, 2015"
output: html_document
---

##**Step 1:** Load the required packages and data

```{r}


source('../01 Data/Load_Packages.R', echo = TRUE)
source('../01 Data/Load_Data.R', echo = TRUE)


```

##**Step 2:** Display a subset of the dataframe

###Mortgage Backed Security #1 Data
```{r}

tbl_df(MBSDF)

```

###Mortgage Backed Security #2 Data
```{r}

tbl_df(MBS2DF)

```

###Mortgage Backed Security Combined Data
```{r}

MBSALLDF <- bind_rows(MBSDF, MBS2DF)
tbl_df(MBSALLDF)

```

###Unemployment Data by State in 2007
```{r}

tbl_df(UNEMPLOYMENTDF)

```

##**Step 3:** Display 3 Interesting Data Wrangling Sets / Visualizations

###Chart 1
This chart compares the state unemployment rate with average mortgage interest rate from the combined data set of 2 mortgage backed securities
```{r}

source("../02 Data Wrangling/DataWrangling1 - chart.R", echo = TRUE)
source("../03 Visualizations/DataWrangling1 - visualization.R", echo = TRUE)


```

###Chart 2
This chart 
```{r}

source("../02 Data Wrangling/DataWrangling2 - chart.R", echo = TRUE)
source("../03 Visualizations/DataWrangling2 - visualization.R", echo = TRUE)

```

###Chart 3
This chart filters the loans for the top 50% according to the rate and then graphs CLTV vs. Unempoyment

```{r}

source("../02 Data Wrangling/DataWrangling3 - chart.R", echo = TRUE)
source("../03 Visualizations/DataWrangling3 - visualization.R", echo = TRUE)

```

##**Step 4:** Create a PNG image that shows a characterization of the categorical columns (as group by plots) and measure columns (as histograms) for our main table


```{r}

source("../03 Visualizations/Categorical.R", echo = TRUE)

```